\chapter{Bibliography}
\begin{enumerate}

\item DTU Compute. “Reading the Reader”. In: \textit{DTU Compute Research} (2025). URL: \url{https://people.compute.dtu.dk/pgba/research/reading-the-reader/}.

\item Jensen, Helena Eschricht; Ilyas, Chaudhary Muhammad Aqdus; Tashk, Ashkan; Cooreman, Bart; Beier, Sofie; Bækgaard, Per. “Context Preservation in Adaptive Reading Systems”. In: \textit{Proceedings of the ACM Symposium on Eye Tracking Research \& Applications (ETRA 2025)} (2025). URL: \url{https://orbit.dtu.dk/files/406853513/3715669.3725897.pdf}.

\item Tobii Pro. “Tobii Pro Fusion”. In: \textit{Tobii Pro Product Page} (2025). URL: \url{https://www.tobii.com/products/eye-trackers/screen-based/tobii-pro-fusion}.

\item SR Research. “EyeLink 1000 Plus”. In: \textit{SR Research Product Page} (2025). URL: \url{https://www.sr-research.com/eyelink-1000-plus/}.

\item SR Research. “EyeLink 1000 Plus – Request a Quote”. In: \textit{SR Research} (2025). URL: \url{https://www.sr-research.com/request-a-quote/eyelink-1000-plus-request-a-quote/}.

\item GazePoint. “GazePoint GP3 HD – Shop Page”. In: \textit{GazePoint Official Store} (2025). URL: \url{https://www.gazept.com/shop/}.

\item Pupil Labs. “Neon Eye Tracking Platform”. In: \textit{Pupil Labs Product Page} (2025). URL: \url{https://pupil-labs.com/products/neon}.

\item RealEye. “RealEye Pricing – Support Documentation”. In: \textit{RealEye Support} (2025). URL: \url{https://support.realeye.io/realeye-pricing}.

\item RealEye. “RealEye Pricing”. In: \textit{RealEye Official Website} (2025). URL: \url{https://www.realeye.io/pricing}.

\item Tobii Pro. “Tobii Pro Lab”. In: \textit{Tobii Pro Software Page} (2025). URL: \url{https://www.tobii.com/products/software/behavior-research-software/tobii-pro-lab}.

\item Lexplore. “Lexplore Assessment”. In: \textit{Lexplore Official Website} (2025). URL: \url{https://lexplore.com/lexplore-assessment}.

\item Lexplore. “Lexplore Pricing”. In: \textit{Lexplore Official Website} (2025). URL: \url{https://lexplore.com/pricing-lexplore}.

\item OrCam. “OrCam Read 3”. In: \textit{OrCam Official Website} (2025). URL: \url{https://www.orcam.com/en-us/orcam-read-3-new}.

\item Microsoft. “Use Immersive Reader in Word”. In: \textit{Microsoft Support} (2025). URL: \url{https://support.microsoft.com/en-au/office/use-immersive-reader-in-word-a857949f-c91e-4c97-977c-a4efcaf9b3c1}.

\item Amazon. “Kindle Text Display Settings”. In: \textit{Amazon Help \& Customer Service} (2025). URL: \url{https://www.amazon.com/gp/help/customer/display.html?nodeId=T5Y94BzSCGwm0vd75W}.

\end{enumerate}